---
title: "linear model from Web"
author: "Kaylie Fagoaga"
date: "Summer 2024"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS

## Descriptive Results --- Scatterplot 

```{r}
plot(ARM~SIMS,data=data)
```

This plot shows that as arm strength increases , sims scores increase too  


### Numerical results


### Inferential  (Build model.1)

#### Predict at target point


#### scatterplot with model fit
  

## Model 2 SIM~GRIP

### Now add in scatterplot


### Numerical results 


### Inferential  (Build model.2)
  

#### predict model.2 at target point

#### now add the model fit to our plot for model.2
  


## Model 3 SIM~ARM+GRIP
prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM.  

```{r}
advNN <- ggplot(davisdata,aes(y=Height,x=dadheight,z=momheight))
```
```{r}
model.2 <- lm(Height~dadheight + momheight,data=davisdata)
summary.lm(model.2)
``` 



### Numerical results (cor)
```{r}
df=data.frame(SIMS=data$SIMS,GRIP=data$GRIP,ARM=data$ARM)
cor(df)
```

Correlation matrix shows that SIMS correlatees with GRIP and ARM, also that 

`
  
### Inferential  (Build 2-dimentional model.3)
```{r}
model.3=lm(SIMS~ARM+GRIP,data=data)
summary.lm(model.3)
```

p-value from the F-statistic is 0.0000000000000002.2, this means that the data fits the model and    
p-values for the model parameters: intercept, coefficient of ARM and coefficiant of GRIP   
each paramenter is significantly 
#### predict model.3 at target point
prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM.

```{r}
newdata = data.frame(GRIP=94, ARM=88)
predSIMS = predict(model.3, newdata, interval = 'pred')
print(predSIMS)
```

The predicted SIMS score for GRIP=94, ARM=88 is 0.150


## Comparing nested models ANOVA Test

### Model.1 vs Model.3
```{r}
model.1.1=lm(SIMS~ARM,data=data0)
anova(model.1, model.3)
summary.lm(model.1)
```



### Model.2 vs Model.3

## Informally compare Model.1 with model.2

